---
title: "RDD_Positive affect labeling"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(dplyr)
library(ggplot2)
library(rddtools)
library(magrittr)
library("xlsx")
library("lfe")
```


```{r}
#load files
rdd_pos <- read.csv("new/rdd_pos.csv") #replies are to affect labelling tweets
rdd_pos_reply <- read.csv("new/rdd_pos_unreply.csv")#replies are not to affect labelling tweets
rdd_pos_unreply <- read.csv("new/rdd_pos_overall_unreply.csv")
```

```{r}
# recenter time varibale
rdd_pos["running_variable"] =rdd_pos["start_t"] - rdd_pos["reply_time"]
rdd_pos_reply["running_variable"] =rdd_pos_reply["start_t"] - rdd_pos_reply["reply_time"]
rdd_pos_unreply["running_variable"] = rdd_pos_unreply["start_t"] # no reply time for unreply
# Add dummy variable
rdd_pos <- rdd_pos %>% 
  mutate(D = as.factor(ifelse(start_t >= reply_time, 1, 0)) ) %>%
  mutate(valence = as.factor(ifelse(mood > 0, "pos", "neg")))
rdd_pos_reply <- rdd_pos_reply %>% 
  mutate(D = as.factor(ifelse(start_t >= reply_time, 1, 0)) ) %>%
  mutate(valence = as.factor(ifelse(mood > 0, "pos0", "neg0")))

rdd_pos_unreply <- rdd_pos_unreply %>% 
  mutate(D = as.factor(ifelse(start_t >= 0, 1, 0)) ) 

rdd_pos_unreply$mood <- 0
rdd_pos_unreply$valence <- "None"

rdd_pos_overall <- rbind(rdd_pos,rdd_pos_reply,rdd_pos_unreply)
```

# Overall Analysis
```{r}
rdd_pos_overall$valence <- relevel(rdd_pos_overall$valence ,ref = "None")
mod <- felm(mean ~ D + running_variable + valence*D +valence*running_variable| as.numeric(reply_time) + as.numeric(followers_count)| 0 |reply_time + followers_count,data = rdd_pos_overall)
summary(mod)

```

## With affect labelling replies

```{r}
mod <- felm(mean ~ D + running_variable + valence*D +valence*running_variable| as.numeric(reply_time) + as.numeric(followers_count)| 0 |reply_time + followers_count,data = rdd_pos)

summary(mod)
```

### Positive replies towards affect labelling tweets
```{r}
rdd_pos_pos <- rdd_pos[rdd_pos["valence"] == "pos",]

mod <- felm(mean ~ D + running_variable |as.numeric(reply_time) + as.numeric(followers_count)| 0 |reply_time + followers_count ,data = rdd_pos_pos)

summary(mod)
```

### Negative replies towards affect labelling tweets
```{r}
rdd_pos_neg <- rdd_pos[rdd_pos["valence"] == "neg",]

mod <- felm(mean ~ D + running_variable |as.numeric(reply_time) + as.numeric(followers_count)| 0 |reply_time + followers_count ,data = rdd_pos_neg)

summary(mod)
```

## Replies but not to affect labelling tweets
```{r}
mod<- felm(mean ~ D + running_variable + valence * D + valence*running_variable|as.numeric(reply_time) + as.numeric(followers_count)| 0 |reply_time + followers_count ,data = rdd_pos_reply)

summary(mod)
```


### Negative replies
```{r}
rdd_pos_reply_neg <- rdd_pos_reply[rdd_pos_reply["valence"] == "neg0",]
mod<- felm(mean ~ D + running_variable|as.numeric(reply_time) + as.numeric(followers_count)| 0 |reply_time + followers_count ,data = rdd_pos_reply_neg)

summary(mod)
```


### Positive replies
```{r}
rdd_pos_reply_pos <- rdd_pos_reply[rdd_pos_reply["valence"] == "pos0",]
mod<- felm(mean ~ D + running_variable|as.numeric(reply_time) + as.numeric(followers_count)| 0 |reply_time + followers_count ,data = rdd_pos_reply_pos)

summary(mod)
```

## Without replies
```{r}
mod<- felm(mean ~ D + running_variable |as.numeric(followers_count)| 0 | followers_count ,data = rdd_pos_unreply)

summary(mod)
```


## Data distribution for replies to affect labelling tweets
```{r}
frequency_mood <- rdd_pos %>%
  group_by(id) %>%
  select(id,valence,mood,reply_time) %>%
  distinct() %>%
  ungroup(id)

frequency_mood %>%
  select(valence) %>%
  group_by(valence) %>%
  count()

frequency_mood  %>%
  group_by(valence) %>%
  summarise_at(vars(mood), list(name = mean))

frequency_mood  %>%
  group_by(valence) %>%
  summarise_at(vars(reply_time), list(name = mean))
```
## Data distribution for replies not  affect labelling tweets
```{r}
frequency_mood <- rdd_pos_reply %>%
  group_by(id) %>%
  select(id,valence,mood,reply_time) %>%
  distinct() %>%
  ungroup(id)

frequency_mood %>%
  select(valence) %>%
  group_by(valence) %>%
  count()

frequency_mood  %>%
  group_by(valence) %>%
  summarise_at(vars(mood), list(name = mean))

frequency_mood  %>%
  group_by(valence) %>%
  summarise_at(vars(reply_time), list(name = mean))
```
